The goal of this work was to implement REST framework for faster development of
applications (mainly web) in modern language, in order to drastically decrease
development time, and growing complexity and by taking the responsibility of
some design decisions. By moving the burden of creating popular modules for
setting proper headers, authentication mechanism and so on, development o web
application based on this framework is much easier and less time consuming
comparing to starting every time from scratch which multiplies by the number of
projects created.

Architecture was designed in a such a way that encourages developers to create
new plugins for some more specific tasks. Further development of this framework
can bring new ones by the means of not breaking the existing functionality
which is an important factor for long-lived applications. Current API and model
is considered stable. The breakage might be introduced only by a new major
versions.

Framework was extensively tested in a production application where it proves
itself as a trusted, stable and well performed solution that scales for many
users. The applications that was created based on this work is used for
exchanging photos between clients and photographers, so pictures can be printed
on a paper and send back to the clients. There is a lot of traffic involved
during upload of those photos, yet it scales very well. Both mobile (Android)
and web application consumes resources exposed by the created framework. By no
means it should be very secure so no leakage of private photos will be
possible.

Example architecture for testing environment was proposed in order to leverage
communication between clients and servers of the main, central server. It can
be further modified by adding new servers or providing additional layers
depends on needs. The REST prove itself in this scenario as fast and reliable
method of communication.

Framework was created in Go for everyone to use free of charge. Anyone can
extend it by writing new custom middlewares or contribute to core of it. Most
important code fragments were described. This also demonstrates how is easy is
to create simple communication mechanism implemented in fairly new language
with well designed standard library.

During the work, author of this project struggled a lot with unit testing, but
finally he made it through. After the hassle, simple and beautiful framework
emerged and all the requirements and expectations have been met.
