Every project needs to define its goals in advance. They should be very
carefully crafted. It may sometimes take a lot of time do that, but this time
will not be wasted. This is crucial from a business point of view and further
implementation. Imagine a situation when an application is half-finished and
goals changed so dramatically that you need to start again from the scratch.
This is causing both money lose and big drop of motivation of the persons who
are working to make those goals a final product. REST forces some design goals
that can take off from shoulders a lot of possible mistakes in first phases of
project design.

\section{Functionality and motivation to create}
Communications between nodes. What does it really mean? What is node? And why
should I care.

First of all let me explain what a node really is. Think about it as a some
sort of independent processing unit that can either act like a client (e.g.\
user browsing Internet) or server (either physical or virtual). Then imagine
that those nodes wants to pass some messages one to another, but they are only
connected through Internet and they might be far away from each other.

There are many ways to solve this problem, but there are some aspects that one
should really care about.


\begin{itemize}
\item Security, you do not want someone eavesdropping you and what is more
  important you need to know that you speaking with the right node. Imagine a
  situation when someone is telling you that your mother is dying just to fish
  you into some dangerous situation, while this is all lie.

\item Reliability, you got something important to say, but the server is down.
  You are left with you car and 2000 km to pass through.

\item Performance, you do not want additional overhead, because you want to
  handle as much nodes as you can.
\end{itemize}

Ease of implementation and well defined API\@. There are few possibilities of
employing such requirements.
\begin{itemize}
\item Distributed messaging
\item WebSockets
\item Sockets
\item REST
\end{itemize}

Let us first focus on distributed messaging. The message passing is done by
different kind of sockets (e.g. Unix, TCP) and there are many software on the
market that deals with all the complexity well. It really works great when you
deal with communication between components that are usually called
micro-services on the same or remote node. Yet there is no possibility of
implementing it in user browser as our goal is to have the same communication
method for clients as well as servers.

WebSockets are kind of a new technique of full-duplex communication over TCP\@.
They were standardized in 2011\cite{WebSockets-wiki}, but they are mature
enough for production usage proved by many big companies. Performance for long
standing connection is really good and it can be easily secured. The main
application is real time data acquisition like stocks price variations which is
not our goal, yet this technology also full fills our requirements.

Sockets similarly to distributed messaging are not supported by web browsers.
It's a little bit harder to secure this kind of linkage too, yet they prove
their usefulness in server to server communication where they are broadly used.

Finally we move to REST which is a software architecture style that can be
easily employed in client-server and server-server communication. The
communication is usually performed over HTTP and that will be in our case.

The purpose of this work is to show how easily we can establish secure
connection between multiple nodes, how we can create powerful authentication
and authorization system and how to scale multiple connections with simple load
balancer. Also I created simple framework written in Go for kick starting
development. I tried to keep code clean with a lot of meaningful comments and
high percentage of tests coverage.

The whole system contains one central server (main) with load balancer for
clients and servers that the main server will connect to in order to obtain
some information.


\section{Software development process}
All code was created in Test-driven development which is a software development
process\cite{TDD} that has origin in extreme programming. The outcome of using
this techniques is to make developer more efficient and more confident and to
make the resulting code better tested, with fewer bugs.

The development cycle could be divided into a few simple steps.
\begin{enumerate}
    \item Create a unit test.
    \item Run test to see if it fail.

        If the test will not fail that means there is a problem with test
        runner or the test does not verify anything.
    \item Write a minimum code that satisfies the test.

        Even hardcoded solution can work here. In next iteration the test could
        be more complicated or verify more than one case.
    \item Run tests again.

        If the test failed the code created in the previous step should be
        fixed. It could happen that the test is broken, hence needs to be fixed
        as well.
    \item Refactor the code.

        Refactoring is important. Some common parts could be moved to common
        places to avoid repetition. Dead code should be removed and so on.
    \item Repeat all the above steps.

        Until the whole assumed functionality is complete.
\end{enumerate}


\section{Implementation environment}
For the purpose of this thesis I used Go compiler for compiling the framework
to binary file as it is written in that language and popular editor Vim for
editing source code files. Tests were written also in Go using testing package
from standard Go library. Gorilla was used as a more advanced http router than
the one in Go standard library. As a version control system for tracking source
code changes I used well-know and battle-tested Git.
